---
title: "Five Parameters"
format: html
author: Alan Tao
execute:
  echo: false
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
```


My question is: How long do political candidates live after the election? I have examined the preceptor table and validity. One problem is that the birth and death dates of losing candidates aren't well documented. I have also examined the population table, stability, representativeness and unconfoundedness. One problem is that only two candidates are documented each year. I then made a model with the equation lived_after = sex * election_age.

$$ lived\_after_i =  \beta_0 + \beta_1 male_i + \beta_2 c\_election\_age_i + 
\\ \beta_3 male_i *  c\_election\_age_i + \epsilon_i $$


```{r}
#| label: model
#| cache: true


df1 <-
  governors |>
  select(last_name, year, state, sex, lived_after, election_age)

fit_all <- brm(
  data = df1,
  formula = lived_after ~ sex * election_age,
  silent = 2,
  refresh = 0,
  seed = 13
)

fit_all
```
